---
title: "p8105_hw1_zg2486"
output: github_document
date: "2024-09-13"
---

# Problem 1

1. The data in the dataset:
```{r, message = FALSE}
library(tidyverse)

data("penguins", package = "palmerpenguins") 
  summary(penguins)
```
There are 3 species of penguins, 3 islands, 2 missing values for bill length, bill depth, flipper length, and body mass, sex (165 female, 168 male, and 11 missing values), year (2007 - 2009).

2. The size of the dataset:

```{r}
nrow(penguins)
ncol(penguins)
```
There are 344 rows and 8 columns in this dataset.
 
3. The mean flipper length:
```{r}
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```
The mean flipper length = 200.9152 mm.
 
4. Make and save the scatterplot of flipper length vs bill length:
```{r}
penguins_plot <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, colour = species))+ geom_point()
  
ggsave("penguins.png", plot = penguins_plot) 
```


# Problem 2

```{r}
set.seed(100)
  hw1_df = tibble(
    norm_samp = rnorm(n = 10),
    vec_logical = norm_samp > 0,
    vec_char = c("A","B","C","D","E","F","G","H","I","J"),
    vec_factor = factor(c("IN","NJ","NY","IN","IN","NJ","NJ","NY","NY","NJ"))
  )

  hw1_df
  
  mean(pull(hw1_df, norm_samp))
  mean(pull(hw1_df, vec_logical))
  mean(pull(hw1_df, vec_char))
  mean(pull(hw1_df, vec_factor))
```
We can get the mean of norm_samp, which is -0.018, and the mean of vec_logical, which is 0.5. We cannot get the mean of vec_char and vec_factor.

```{r eval=FALSE}
as.numeric(pull(hw1_df,vec_logical))
as.numeric(pull(hw1_df,vec_char))
as.numeric(pull(hw1_df,vec_factor))
```
The logical vector will convert to 0 and 1, and this can help to explain why we get the mean of 0.5 for this vector. Character vector was converted to 'NA', which make sense that it can't be used to calculate the mean. The factor vector will be convert to 1, 2, 3, which just represent the level of the vector, not mean the value of each level of factor are 1, 2, 3, so that help to explain why we can't get the mean of this vector.
